### 2019-04-15 manuscript.tex
Autocommit (fgc)

\usepackage{longtable,booktabs}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

>>>>

\usepackage{longtable,booktabs}
\usepackage{graphicx}
\usepackage{grffile}
\IfFileExists{parskip.sty}{%
\usepackage{parskip}
}{% else
\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}
% Redefines (sub)paragraphs to behave more like sections
\ifx\paragraph\undefined\else
\let\oldparagraph\paragraph
\renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
\let\oldsubparagraph\subparagraph
\renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi

@@

\FloatBarrier

\section{Figures}

\subsection{Daughter Plan}
\begin{center}
\begin{figure}[h!]
\includegraphics[scale=0.7]{./git_push/daughterPlan_effects_plot.Rout.pdf}
\end{figure}
\end{center}

\begin{center}
\begin{figure}[h!]
\includegraphics[scale=0.7]{./git_push/daughterPlan_isoplots.Rout.pdf}
\end{figure}
\end{center}

\newpage

\subsection{FGC Persistence}
\begin{center}
\begin{figure}[h!]
\includegraphics[scale=0.7]{./git_push/fgcPersist_effects_plot.Rout.pdf}
\end{figure}
\end{center}

\begin{center}
\begin{figure}[h!]
\includegraphics[scale=0.7]{./git_push/fgcPersist_isoplots.Rout.pdf}
\end{figure}
\end{center}

\newpage

\subsection{Hybrid Model}
\begin{center}
\begin{figure}[h!]
\includegraphics[scale=0.7]{./git_push/hybrid_effects_plot.Rout.pdf}
\end{figure}
\end{center}

\begin{center}
\begin{figure}[h!]
\includegraphics[scale=0.7]{./git_push/hybrid_isoplots.Rout.pdf}
\end{figure}
\end{center}

\FloatBarrier
